%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}

\usepackage{enumitem}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{}{Jack Deadman}{
%\href{mailto:}{jackdeadman1@gmail.ac.uk}
Award winning graduate with experience in working in teams to deliver high quality software to solve real world problems.

}

\vspace{0pt}{

%A research focused student with an interest in speech and audio processing, experience in delivering high quality solutions to solve real world problems.
%Award winning graduate with experience in working in teams to deliver high quality software to solve real world challenges.
}


%\namesection{Jack}{Deadman}{ \urlstyle{same}\url{http://jackdeadman.com}}
%\href{mailto:}{jdeadman1@sheffield.ac.uk}
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{University of Sheffield}
\descript{MComp in Computer Science}
\location{First Class (Hons).}
\location{Year 1: 82.1\%}
\location{Year 2: 82.7\%}
\location{Year 3: 83.2\%}
\location{Year 4: 79.5\%}
\sectionsep

\subsection{Sussex Downs College}
\location{Software Development: Distinction*}
\location{Computing: A}
\location{Mathematics: B}
\sectionsep

\subsection{Bishop Bell School}
\location{11 GCSEs A*-C including Maths and English.}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
Github:// \href{https://github.com/jackdeadman}{\custombold{jackdeadman}} \\
LinkedIn://  \href{https://www.linkedin.com/in/jack-deadman-19101297}{\custombold{jackdeadman}} \\
Twitter://  \href{https://twitter.com/jackdeadman96}{\custombold{@jackdeadman96}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\subsection{University}
Sound Event Detection\\
Open GL 3D Graphics Scene\\
Genesys and Software Hut \textit{(Software Engineering modules with real client)}
\sectionsep
\subsection{Side Projects}
Natural Deduction tool\\
Quad (Custom Linux login screen)\\
Chat client with \LaTeX \ support\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Skilled:}
Java \textbullet{} JavaScript \textbullet{} Ruby\\
Rails \textbullet{} Python \textbullet{} Numpy\\
CSS \textbullet{} Sass \textbullet{} \LaTeX\ \\
PHP \textbullet{} React  \textbullet{} Node \\
\location{Familiar:}
Bash \textbullet{} Haskell \textbullet{} Prolog \textbullet{} C
\sectionsep

\subsection{Non-Technical}
Teaching\\
Presenting\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{University of Sheffield}
\descript{| Postgraduate Researcher }
\location{September 2018 – Present}

%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{enumerate}[leftmargin=0.4cm, itemsep=-0.3ex, topsep=0pt]
\item[--] Working in the Speech and Hearing group under the supervision of Prof. Jon Barker researching applying video information to inform beamforming algorithms for pre-processing in automatic speech recognition.
\end{enumerate}
\sectionsep

\runsubsection{University of Sheffield}
\descript{| Summer Research Intern }
\location{June 2017 – July 2017}

\begin{enumerate}[leftmargin=0.4cm, itemsep=-0.3ex, topsep=0pt]
\item[--] Worked in the Testing and Security research group under the supervision of Dr. Achim Brucker developing analysis tools to detect malicious browser extensions.
\item[--] Successfully deployed the software on around 60,000 browser extensions using the Univesity's high performance computing facility.
\item[--] Successfully finished an academic paper reporting our results.
\end{enumerate}
\sectionsep

\runsubsection{Visual Wind}
\descript{| Software Engineer }
\location{June 2016 – Sep 2016}
\begin{enumerate}[leftmargin=0.4cm, itemsep=-0.3ex, topsep=0pt]
\item[--] Worked as part of a small team of people to produce visualisation software for wind turbines.
\item[--] Introduced agile methodologies into the company.
\item[--] Produced a proof of concept application which successfully aided a joint venture secure funding.
\end{enumerate}
\sectionsep


\runsubsection{University of Sheffield}
\descript{| Student Ambassador}
\location{December 2015 – June 2018}
\begin{enumerate}[leftmargin=0.4cm, itemsep=-0.3ex, topsep=0pt]
%\item[--] Introduce prospective students to the University on open days and assist lecturers during outreach events.
\item[--] Regularly gave a 15 minute presentation to a group of around 15 students explaining what University life is like and answered queries they have.
\end{enumerate}
\sectionsep

\runsubsection{University of Sheffield}
\descript{| Student Teaching Assistant}
\location{September 2016 – Present}
\begin{enumerate}[leftmargin=0.4cm, itemsep=-0.3ex, topsep=0pt]
\item[--] Assist in teaching undergraduate lab sessions.
\item[--] Invigilate assessments.
\item[--] Mark undergraduate assignments.
\end{enumerate}
\sectionsep

\runsubsection{University of Sheffield}
\descript{| Support Worker}
\location{September 2017 – Present}
\begin{enumerate}[leftmargin=0.4cm, itemsep=-0.3ex, topsep=0pt]
\item[--] Take lecture notes for a visually impaired individual as well as assist their learning by explaining visual concepts and mathematical equations.
\end{enumerate}
\sectionsep

\runsubsection{University of Sheffield}
\descript{| Mentor}
\location{September 2016 – June 2018}
\begin{enumerate}[lefftmargin=0.4cm, itemsep=-0.3ex, topsep=0pt]
\item[--] As a welfare mentor I helped students settle into University as they transition into a new environment. As a programming mentor I helped student settle in to Univesity academically.
%\item[--] Successfully helped 6 individuals settle in with University life whilst being a welfare mentor.
%\item[--] Successfully helped 2 individuals with programming difficulties whist being a programming mentor as part of the Computer Science society.
\end{enumerate}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards}
\begin{tabular}{rll}
2018	     & Full Ph.D scholarship & EPSRC\\
2018	     & Mappin Medal & University of Sheffield\\
2017	     & Summer Research Scholarship & EPSRC\\
2017	     & Highly Commended paper in Computer Science & The Undergraduate awards\\
2016	     & Winning team in "Software Hut" module  & Prize chosen by client \\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\end{document}  \documentclass[]{article}
